Reproduction Survey Analysis

### 2022-11-09 procedure/code/203_results.Rmd
Latest coding updates to produce analysis file.

```{r load}
survey_resp <- readRDS(here("data", "derived", "public", "survey_resp.RDS"))
summary(survey_resp)
```

@@

```{r sub-fields-by-methods}
# crosstab sub-fields and methods
addmargins(table(survey_resp$Q4, survey_resp$Q3))
```

@@

```{r familiarity-by-subfield}
addmargins(table(survey_resp$Q5, survey_resp$Q3))
```

@@

```{r define-reproducibility}
# how did folks define "reproducibility" ?
survey_resp %>% select(Q3, Q4, Q5, Q6) %>%
  filter(Q5 != "Not at all") %>%
  arrange(Q5, Q4) %>%
  write.csv(here("results", "tables", "definitions.csv"))
```

@@

```{r familiarity-by-subfield}
group_by(survey_resp, Q3) %>%
  summarise(
    count = n(),
    mean = round(mean(familiar, na.rm = TRUE),2),
    sd = round(sd(familiar, na.rm = TRUE),2)
  )
```

@@

```{r familiarity-by-subfield-anova}
aov(familiar ~ Q3, data=survey_resp) %>% summary()
```

>>>>

```{r load}
survey_resp <- readRDS(here("data","derived","public","analysis_hegs_rpr.rds"))
summary(survey_resp)
```

@@

```{r sub-fields-by-methods}
# crosstab sub-fields and methods
addmargins(table(survey_resp$Q3_recoded, survey_resp$Q4))
```

@@

```{r familiarity-by-subfield}
addmargins(table(survey_resp$Q5, survey_resp$Q3_recoded))
```

@@

```{r define-reproducibility}
# how did folks define "reproducibility" ?
survey_resp %>% select(Q3_recoded, Q4, Q5, Q6) %>%
  filter(Q5 != "Not at all") %>%
  arrange(Q5, Q4) %>%
  write.csv(here("results", "tables", "definitions.csv"))
```

@@

```{r familiarity-by-subfield}
group_by(survey_resp, Q3_recoded) %>%
  summarise(
    count = n(),
    mean = round(mean(familiar, na.rm = TRUE),2),
    sd = round(sd(familiar, na.rm = TRUE),2)
  )
```

@@

```{r familiarity-by-subfield-anova}
aov(familiar ~ Q3_recoded, data=survey_resp) %>% summary()
```
